Structured Versus Decorated Cospans

### 2021-06-17 cospans_new.tex
started work on Thm. 2.5 - don't look at it yet.

\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm}
\usepackage{comment}
\usepackage[neveradjust]{paralist}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage[outline]{contour}
\contourlength{1.2pt}
\usepackage{tikz}
\usetikzlibrary{intersections,arrows.meta,calc,quotes,math,decorations.pathreplacing,decorations.markings,cd,arrows,positioning,fit,matrix,
shapes.geometric,external,decorations.pathmorphing,backgrounds,circuits,circuits.ee.IEC,shapes}
\usepackage[a4paper,top=3cm,bottom=3cm,inner=3cm,outer=3cm]{geometry}
\usepackage[foot]{amsaddr}
\usepackage{graphicx}
\usepackage{stackrel}

@@

We start with decorated cospans, proving Theorems \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built
from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.    The Grothendieck construction gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations $U \maps \inta F \to \A$.  We need two refinements of this construction: one that gives monoidal ofibrations, and one that gives symmetric monoidal opfibrations.  We explain the Grothendieck construction and these related concepts in \cref{subsec:fibrations}; here we simply recall the result we need.

@@

Our construction gives not only decorated cospan double categories, but  also maps between these: that is, symmetric monoidal double functors, as in \cref{def:doublefun}. Suppose we have two categories $\A,\A'$ with finite colimits and two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.    Then we can obtain a map between their decorated cospan double categories, $\lH \maps F\lCsp \to F' \lCsp$, from:

@@

\item a symmetric lax monoidal pseudofunctor $(E,\phi,\phi_0) \maps \Cat \to \Cat$, 

@@

The induced double functor $\lH \maps F\lCsp \to F'\lCsp$ is defined as follows:

@@

\item The image of an $F$-decorated cospan $M$ in $F\lCsp$ is the $F'$-decorated cospan $\lH(M)$ in $F'\lCsp$
\begin{align*}
 M=\left(a\xrightarrow{i}m\xleftarrow{o}b,x\in F(m)\right)\mapsto \lH(M)=\left(H(a)\xrightarrow{H(i)}H(m)\xleftarrow{H(o)}H(b),\bar{x}\in F'(H(m))\right)& \textrm{ where } \\
\bar{x}:=\one \xrightarrow{\phi_0} E(\one) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)) &
\end{align*}
\item The image of a map of decorated cospans $\alpha \maps M \to N$ in $F\lCsp$ is the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$

@@

%\node (G) at (1,-1) {$\tau \maps F(h)(x) \to x'$};

@@

\node (H) at (3.75,0) {$\mapsto$};

@@

(B) edge node [left] {$h$} (D)

@@

where a decoration morphism $\tau \maps F(h)(x) \to x'$ is mapped to a 
decoration morphism as follows:

@@

\begin{thm}
\label{thm:functoriality}
Given two categories $\A$ and $\A'$ with finite colimits, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a natural isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[below]{$F'$} (D);
\end{tikzpicture}
\] 
the triple $(H,E,\theta)$ induces a symmetric monoidal double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
\end{thm}

\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}.

From the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$, we can obtain a Beck-Chevalley symmetric monoidal opfibration $\Phi \maps (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}, where $U \maps \int F \to \A$ is the associated monoidal opfibration of the pseudofunctor $F$. We can do the same for the other symmetric lax monoidal pseudofunctor $F' \maps \A' \to \Cat$ to obtain another Beck-Chevalley symmetric monoidal opfibration $\Phi' \maps (\A'/U') \to \A'$.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)$};
\node (B) at (2,0) {$(\A'/U')$};
\node (C) at (0,-1.5) {$\A$};
\node (D) at (2,-1.5) {$\A'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\Phi$} (C)
(B) edge node[right]{$\Phi'$} (D)
(C) edge node[above]{$H$} (D);
\end{tikzpicture}
\]
We construct a strong monoidal functor $G \maps (\A/U) \to (\A'/U')$ between the monoidal comma categories $(\A/U)$ and $(\A'/U')$ that will make the induced square commute. Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then, by a 2-functor $\mathbb{F}\mathbf{r} \maps \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008}, will yield a map $$\mathbb{F}\mathbf{r}(G,H) \maps \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Phi')= F'\lCsp$.

The monoidal comma category $(\A/U)$ has:
\begin{enumerate}
\item{objects as triples $(a,x,a \to U(x))$, and}
\item{a morphism from $(a,x,a \to U(x))$ to $(b,y,b \to U(y))$ is a pair of morphisms $f \maps a \to b$ and $\tau \maps x \to y$ that make the following square commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$b$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1,-1) {$U(y)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$U(\tau)$} (D);
\end{tikzpicture}
\]
}
\end{enumerate}
The tensor product of two objects $(a_1,x_1,a_1 \to U(x_1))$ and $(a_2,x_2,a_2 \to U(x_2))$ is given by $$(a_1,x_1,a_1 \to U(x_1)) \otimes (a_2,x_2,a_2 \to U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \to U(x_1 \otimes x_2)).$$The monoidal unit of $(\A/U)$ is given by $(0_\A,0_\X,0_\A \to U(0_\X))$. Those of $(\A'/U')$ are analogous.

On objects, the strong monoidal functor $F \maps (\A/U) \to (\A'/U')$ is defined as follows:
\begin{enumerate}
\item{given $(a,x,a \to U(x))$ in $(\A/U)$ where $x=(m,p) \in \A \times F(m)$, $$G(a,x,a \to U(x)) = (H(a),\theta_m E(p) \phi,H(a) \to U'(\theta_m E(p) \phi))$$ where $\theta_m E(p) \phi$ is given by 
$$1 \xrightarrow{\phi} E(1) \xrightarrow{E(p)} E(F(m)) \xrightarrow{\theta_m} F'(H(m))$$
so that $U'(\theta_m E(p) \phi)=H(m)$, }
\item{given a pair of morphisms $(f,\tau)$ that make the following square commute:
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1,-1) {$U(y)$};
(A) edge node[left]{$$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$U(\tau)$} (D);
we define $$G(f,\tau)=(H(f),\theta_h E(\tau) \phi).$$
which make the following square in $(\A'/U')$ commute:
\node (A) at (0,0) {$H(a)$};
\node (B) at (3,0) {$H(b)$};
\node (C) at (0,-1) {$U'(\theta_m E(p) \phi)$};
\node (D) at (3,-1) {$U'(\theta_n E(q) \phi))$};
(A) edge node[above]{$H(f)$} (B)
(A) edge node[left]{$$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$U'(\theta_h E(\tau) \phi)$} (D);
where $\tau$ and $\theta_h E(\tau) \phi$ are given respectively by:
(G) edge node [above] {$p$} (H)
(G) edge node [below] {$q$} (I)
(D) edge node [above] {$\theta_n$} (F)
(L) edge node[above]{$E(p)$} (B)
(L) edge node[below]{$E(q)$} (D)
(B) edge node[right]{$E(F(h))$} (D);
\end{enumerate}
The laxator is given by the following natural isomorphism between $\theta_m E(p) \phi \times \theta_n E(q) \phi$ and $\theta_{m+n} E(p \times q) \phi$:
\hspace{-.6in}
\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{p,q}} \cong}$};
\node () at (1.25,-0.5) {$\scriptscriptstyle{\stackrel{\lambda} \cong}$};
\node (L1) at (0.5,0) {$\scriptscriptstyle{1 \times E(1)}$};
\node (L2) at (0.5,-1) {$\scriptscriptstyle{E(1)}$};
\node (K) at (-1,0) {$\scriptscriptstyle{1 \times 1}$};
\node (K2) at (-1,-1) {$\scriptscriptstyle{1}$};
\node (B) at (2,0) {$\scriptscriptstyle{E(1) \times E(1)}$};
\node (D) at (2,-1) {$\scriptscriptstyle{E(1 \times 1)}$};
\node (E) at (4,0) {$\scriptscriptstyle{E(F(m)) \times E(F(n))}$};
\node (F) at (4,-1) {$\scriptscriptstyle{E(F(m) \times F(n))}$};
\node (G) at (7,0) {$\scriptscriptstyle{F'(H(m)) \times F'(H(n))}$};
\node (H) at (10,0) {$\scriptscriptstyle{F'(H(m)+H(n))}$};
\node (I) at (7,-1) {$\scriptscriptstyle{E(F(m+n))}$};
\node (J) at (10,-1) {$\scriptscriptstyle{F'(H(m+n))}$};
(K) edge node [left] {$\lambda$} (K2)
(K) edge node [above] {$1 \times E_0$} (L1)
(K2) edge node [above] {$E_0$} (L2)
(H) edge node [right] {$F'(H_{m,n})$} (J)
(E) edge node [above] {$\theta_m \times \theta_n$} (G)
(G) edge node [above] {$\phi'_{H(m),H(n)}$} (H) 
(F) edge node [above] {$E(\phi_{m,n})$} (I)
(I) edge node [above] {$\theta_{m+n}$} (J)
(B) edge node [above] {$E(p) \times E(q)$} (E)
(D) edge node [above] {$E(p \times q)$} (F)
(E) edge node [right] {$E_{F(m),F(n)}$} (F)
(L1) edge node[above]{$E_0 \times 1$} (B)
(L1) edge node [left] {$\lambda$} (L2)
(L2) edge node[above]{$E(\lambda^{-1})$} (D)
(B) edge node[right]{$E_{1,1}$} (D);
and we also have a natural isomorphism between $0_{\inta F'}$ and $G(0_{\inta F})$ given by:
\node (A) at (-1,0.5) {$\scriptscriptstyle{1}$};
\node () at (4,0.66) {$\scriptscriptstyle{\cong}$};
\node (A1) at (0,0) {$\scriptscriptstyle{E(1)}$};
\node (A2) at (2,0) {$\scriptscriptstyle{E(F(0_\A))}$};
\node (A3) at (4,0) {$\scriptscriptstyle{E(F(0_\A))}$};
\node (A4) at (6,0) {$\scriptscriptstyle{F'(H(0_\A))}$};
\node (A') at (2,0.5) {$\scriptscriptstyle{F'(H(0_\A))}$};
\node (B1) at (0,1) {$\scriptscriptstyle{F'(0_{\A'})}$};
\node (B2) at (6,1) {$\scriptscriptstyle{F'(0_{\A'})}$};
(A) edge node [below] {$\scriptscriptstyle{E_0}$} (A1)
(A) edge node [above] {$\scriptscriptstyle{\phi_0'}$} (B1)
(A1) edge node [above] {$\scriptscriptstyle{E(\phi_0)}$} (A2)
(A2) edge node [below] {$\scriptscriptstyle{E(F(!_{0_\A}))}$} (A3)
(A3) edge node [below] {$\scriptscriptstyle{\theta_{0_\A}}$} (A4)
(A2) edge node [left] {$\scriptscriptstyle{\theta_{0_\A}}$} (A')
(B1) edge node [fill=white] {$\scriptscriptstyle{F'(H_0)}$} (A')
(A') edge node [fill=white] {$\scriptscriptstyle{F'(H(!_{0_\A}))}$} (A4)
(B2) edge node [right] {$\scriptscriptstyle{F'(H_0)}$} (A4)
(B1) edge node [above] {$\scriptscriptstyle{F'(!_{0_{\A'}})}$} (B2);
One can show that this laxator and unit morphism satisfy the four required coherence laws of a symmetric strong monoidal functor.

>>>>

\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm}
\usepackage{comment}
\usepackage[mathscr]{euscript}
\usepackage[neveradjust]{paralist}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage[outline]{contour}
\contourlength{1.2pt}
\usepackage{tikz}
\usetikzlibrary{intersections,arrows.meta,calc,quotes,math,decorations.pathreplacing,decorations.markings,cd,arrows,positioning,fit,matrix,
shapes.geometric,external,decorations.pathmorphing,backgrounds,circuits,circuits.ee.IEC,shapes}
\usepackage[a4paper,top=3cm,bottom=3cm,inner=3cm,outer=3cm]{geometry}
\usepackage[foot]{amsaddr}
\usepackage{graphicx}
\usepackage{stackrel}

@@

We start with decorated cospans, proving Theorem \ref{thm:decorated_cospans_1} and 
\ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.    The Grothendieck construction gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations $U \maps \inta F \to \A$.  We need two refinements of this construction: one that gives monoidal opfibrations, and one that gives symmetric monoidal opfibrations.  We recall the Grothendieck construction and these related concepts in \cref{subsec:fibrations}; here we simply state the result we need.

@@

Our construction gives not only decorated cospan double categories, but  also maps between these.   For simplicity we only consider the monoidal case.  Suppose we have two categories $\A,\A'$ with finite colimits and two lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.   Then we can obtain a map between their decorated cospan double categories, namely a double functor $\lH \maps F\lCsp \to F' \lCsp$, from:

@@

\item a lax monoidal pseudofunctor $(E,\phi,\phi_0) \maps \Cat \to \Cat$, 

@@

The double functor $\lH \maps F\lCsp \to F'\lCsp$ is defined as follows:

@@

\item The image of an $F$-decorated cospan
\[ M= (a\xrightarrow{i}m\xleftarrow{o}b, \; x\in F(m)) \]
is the following $F'$-decorated cospan:
\[ \lH(M)= (H(a)\xrightarrow{H(i)}H(m)\xleftarrow{H(o)}H(b), \;\bar{x}\in F'(H(m))) \]
 where
\bar{x}:=\one \xrightarrow{\phi_0} E(\one) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).\]
\item The image of a map of decorated cospans in $F\lCsp$ 

@@

\node (G) at (5,0) {$\tau \maps F(h)(x) \to x'$};
(B) edge node [left] {$h$} (D);
is the following map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$:

@@

@@

@@

where the decoration morphism $\tau$ is mapped to a decoration morphism as follows:

@@

\begin{thm}
\label{thm:functoriality}
Given two categories $\A$ and $\A'$ with finite colimits, two lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a natural isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[below]{$F'$} (D);
\end{tikzpicture}
\] 
the triple $(H,E,\theta)$ induces a double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
\end{thm}

\begin{proof}   From the lax monoidal pseudofunctor $F \maps \A \to \Cat$, we obtain a Beck--Chevalley monoidal bifibration $\Phi \maps (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}.  We do the same for the lax monoidal pseudofunctor $F' \maps \A' \to \Cat$ to obtain a Beck--Chevalley monoidal bifibration $\Phi' \maps (\A'/U') \to \A'$.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)$};
\node (B) at (2,0) {$(\A'/U')$};
\node (C) at (0,-1.5) {$\A$};
\node (D) at (2,-1.5) {$\A'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\Phi$} (C)
(B) edge node[right]{$\Phi'$} (D)
(C) edge node[above]{$H$} (D);
\end{tikzpicture}
\]
Next we construct a strong monoidal functor $G \maps \A/U \to \A'/U'$  that makes the resulting square commute.  Such a commutating square is a morphism in Shulman's 2-category $\mathscr{MF}^{\textrm{fr}}$ of Beck--Chevalley monoidal bifibrations.  Appying Shulman's 2-functor $\mathbb{F}\mathbf{r} \maps \mathscr{MF}^{\textrm{fr}} \to \mathscr{F}r\mathscr{B}i$ to this morphism, \cite[Theorem 14.11]{Shulman2008}, we obtain the desired double functor
\[ \mathbb{H} \maps  F\lCsp \to F'\lCsp .\]

We described $\A/U$ and its monoidal structure in the proof of \cref{thm:decorated_cospans_1}, 
and of course the case of $\A'/U'$ is analogous.   We define a strong monoidal functor $G \maps \A/U \to \A'/U'$ as follows.  First suppose we are given a object $(a \xrightarrow{i} b, x)$ in $(\A/U)$, where recall $x \in F(x)$.    Then we define
\[  G(a \xrightarrow{i} b, x) = (H(a) \xrightarrow{H(i)} H(b), x') \]
where the object $x' \in F'(H(b))$ is picked out by the composite
\[  1 \xrightarrow{\phi} E(1) \xrightarrow{E(p)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)) \]
so that $U'(\theta_m E(p) \phi)=H(m)$, 
Given a pair of morphisms $(f,\tau)$ that make the following square commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$b$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1,-1) {$U(y)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$U(\tau)$} (D);
\end{tikzpicture}
\]
we define $$G(f,\tau)=(H(f),\theta_h E(\tau) \phi).$$
which make the following square in $(\A'/U')$ commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$H(a)$};
\node (B) at (3,0) {$H(b)$};
\node (C) at (0,-1) {$U'(\theta_m E(p) \phi)$};
\node (D) at (3,-1) {$U'(\theta_n E(q) \phi))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$H(f)$} (B)
(A) edge node[left]{$$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$U'(\theta_h E(\tau) \phi)$} (D);
\end{tikzpicture}
\]
where $\tau$ and $\theta_h E(\tau) \phi$ are given respectively by:
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-3.5,-0.5) {$1$};
\node (H) at (-2,0) {$F(m)$};
\node (I) at (-2,-1) {$F(n)$};
\node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow\tau$};
\node (A) at (-0.25,-0.5) {$1$};
\node (L) at (0.5,-0.5) {$E(1)$};
\node (B) at (2,0) {$E(F(m))$};
\node (D) at (2,-1) {$E(F(n))$};
\node (C) at (1.5,-0.5) {$\scriptstyle\Downarrow E(\tau)$};
\node (E) at (4,0) {$F^\prime(H(m))$};
\node (F) at (4,-1) {$F^\prime(H(n))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node [above] {$\phi$} (L)
(G) edge node [above] {$p$} (H)
(G) edge node [below] {$q$} (I)
(H) edge node [right] {$F(h)$} (I)
(B) edge node [above] {$\theta_m$} (E)
(D) edge node [above] {$\theta_n$} (F)
(E) edge node [right] {$F'(H(h))$} (F)
(L) edge node[above]{$E(p)$} (B)
(L) edge node[below]{$E(q)$} (D)
(B) edge node[right]{$E(F(h))$} (D);
\end{tikzpicture}
\]

The laxator is given by the following natural isomorphism between $\theta_m E(p) \phi \times \theta_n E(q) \phi$ and $\theta_{m+n} E(p \times q) \phi$:
\[
\begin{tikzpicture}[scale=1.5]
\hspace{-.6in}
\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{p,q}} \cong}$};
\node () at (1.25,-0.5) {$\scriptscriptstyle{\stackrel{\lambda} \cong}$};
\node (L1) at (0.5,0) {$\scriptscriptstyle{1 \times E(1)}$};
\node (L2) at (0.5,-1) {$\scriptscriptstyle{E(1)}$};
\node (K) at (-1,0) {$\scriptscriptstyle{1 \times 1}$};
\node (K2) at (-1,-1) {$\scriptscriptstyle{1}$};
\node (B) at (2,0) {$\scriptscriptstyle{E(1) \times E(1)}$};
\node (D) at (2,-1) {$\scriptscriptstyle{E(1 \times 1)}$};
\node (E) at (4,0) {$\scriptscriptstyle{E(F(m)) \times E(F(n))}$};
\node (F) at (4,-1) {$\scriptscriptstyle{E(F(m) \times F(n))}$};
\node (G) at (7,0) {$\scriptscriptstyle{F'(H(m)) \times F'(H(n))}$};
\node (H) at (10,0) {$\scriptscriptstyle{F'(H(m)+H(n))}$};
\node (I) at (7,-1) {$\scriptscriptstyle{E(F(m+n))}$};
\node (J) at (10,-1) {$\scriptscriptstyle{F'(H(m+n))}$};
\path[->,font=\scriptsize,>=angle 90]
(K) edge node [left] {$\lambda$} (K2)
(K) edge node [above] {$1 \times E_0$} (L1)
(K2) edge node [above] {$E_0$} (L2)
(H) edge node [right] {$F'(H_{m,n})$} (J)
(E) edge node [above] {$\theta_m \times \theta_n$} (G)
(G) edge node [above] {$\phi'_{H(m),H(n)}$} (H) 
(F) edge node [above] {$E(\phi_{m,n})$} (I)
(I) edge node [above] {$\theta_{m+n}$} (J)
(B) edge node [above] {$E(p) \times E(q)$} (E)
(D) edge node [above] {$E(p \times q)$} (F)
(E) edge node [right] {$E_{F(m),F(n)}$} (F)
(L1) edge node[above]{$E_0 \times 1$} (B)
(L1) edge node [left] {$\lambda$} (L2)
(L2) edge node[above]{$E(\lambda^{-1})$} (D)
(B) edge node[right]{$E_{1,1}$} (D);
\end{tikzpicture}
\]
and we also have a natural isomorphism between $0_{\inta F'}$ and $G(0_{\inta F})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (-1,0.5) {$\scriptscriptstyle{1}$};
\node () at (4,0.66) {$\scriptscriptstyle{\cong}$};
\node (A1) at (0,0) {$\scriptscriptstyle{E(1)}$};
\node (A2) at (2,0) {$\scriptscriptstyle{E(F(0_\A))}$};
\node (A3) at (4,0) {$\scriptscriptstyle{E(F(0_\A))}$};
\node (A4) at (6,0) {$\scriptscriptstyle{F'(H(0_\A))}$};
\node (A') at (2,0.5) {$\scriptscriptstyle{F'(H(0_\A))}$};
\node (B1) at (0,1) {$\scriptscriptstyle{F'(0_{\A'})}$};
\node (B2) at (6,1) {$\scriptscriptstyle{F'(0_{\A'})}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node [below] {$\scriptscriptstyle{E_0}$} (A1)
(A) edge node [above] {$\scriptscriptstyle{\phi_0'}$} (B1)
(A1) edge node [above] {$\scriptscriptstyle{E(\phi_0)}$} (A2)
(A2) edge node [below] {$\scriptscriptstyle{E(F(!_{0_\A}))}$} (A3)
(A3) edge node [below] {$\scriptscriptstyle{\theta_{0_\A}}$} (A4)
(A2) edge node [left] {$\scriptscriptstyle{\theta_{0_\A}}$} (A')
(B1) edge node [fill=white] {$\scriptscriptstyle{F'(H_0)}$} (A')
(A') edge node [fill=white] {$\scriptscriptstyle{F'(H(!_{0_\A}))}$} (A4)
(B2) edge node [right] {$\scriptscriptstyle{F'(H_0)}$} (A4)
(B1) edge node [above] {$\scriptscriptstyle{F'(!_{0_{\A'}})}$} (B2);
\end{tikzpicture}
\]
One can show that this laxator and unit morphism satisfy the four required coherence laws of a symmetric strong monoidal functor.
\end{proof}
